---
title: "p8105_hw1_ps3195"
author: "Pengyuan Su"
date: "9/15/2020"
output:
    html_document:
    toc: true
    toc_float: true
---



>

#### **Solution to Homework 1:**



```{r}
library(tidyverse)
```





>### *Problem 1*


Create a data frame comprised of required elements:


```{r dataframe}
prob1_df = tibble(
  samp = rnorm(10),
  samp_gt_0 = samp > 0,
  char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  factor_vec = factor(c("hard", "hard", "hard", "normal", "normal", "normal", "normal", "easy", "easy", "easy"))
)

```



Take the **mean** of each variable in the data frame:


```{r mean_pull_var}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```




The mean of **numbers and logical vector** works while the mean of **character and factor** does not make it.


Convert variables from one type to another:


```{r convert_numeric}
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```


The **logical vector and the factor vector** have been converted to numerical while the **character** failed since they are shown "NA". 

(However, during the converting process of factor, "hard" has been converted to level 1 and "normal" to be level 3 and "easy" to be level 2 )




```{r second_chunk}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(pull(prob1_df, factor_vec)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```

