---
title: "p8105_hw1_ps3195"
author: "Pengyuan Su"
date: "9/15/2020"
output:
    html_document:
    toc: true
    toc_float: true
---



>

#### **Solution to Homework 1:**



```{r library}
library(tidyverse)
```





>### *Problem 1*


Create a data frame comprised of required elements:


```{r dataframe}
prob1_df = tibble(
  samp = rnorm(10),
  samp_gt_0 = samp > 0,
  char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  factor_vec = factor(c("hard", "hard", "hard", "normal", "normal", "normal", "normal", "easy", "easy", "easy"))
)

```



Take the **mean** of each variable in the data frame:


```{r mean_pull_var}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```




The mean of **numbers and logical vector** works while the mean of **character and factor** does not make it.


Convert variables from one type to another:


```{r convert_numeric}
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```


The **logical vector and the factor vector** have been converted to numerical while the **character** failed since they are shown "NA". 

(However, during the converting process of factor, "hard" has been converted to level 1 and "normal" to be level 3 and "easy" to be level 2 )




```{r second_chunk}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(pull(prob1_df, factor_vec)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```


>### *Problem 2*

load the `penguins` dataset:


```{r}
ds = data("penguins", package = "palmerpenguins")
```

The short description of the `penguins` dataset:


The name of this dataset is `r ds`. And there are three factors which are `species`, `island` and `sex`,five numeric vectors which are `bill_length_mm`, `bill_depth_mm`,`flipper_length_mm`, `body_mass_g` and `year`.


The data of `year` is from `r min(pull(penguins, year))` to `r max(pull(penguins, year))`


`r levels(pull(penguins, species))` are the three levels of species, while `r levels(pull(penguins, island))` are the three levels of island. `sex` is divided into `r levels(pull(penguins, sex))`. 


The size of data is: `r nrow(penguins)` rows * `r ncol(penguins)` columns


To calculas the mean of flipper length, we need to delete the NA rows:


```{r delete_NA_rows}
data = na.omit(penguins)
```


Then, the mean of flipper length is `r mean(pull(data, flipper_length_mm))`


The scatterplot is:


```{r scatterplot}
plot_df = tibble(
  x = pull(data, bill_length_mm),
  y = pull(data, flipper_length_mm),
  species = pull(data, species)
)

ggplot(plot_df, aes(x = x, y = y, color = species)) + geom_point()

ggsave("scatter_plot.pdf", height = 6, width = 6)
```

